European or American? A re-examination of the transatlantic influence over the IMF

### 2025-04-22 demo/demo.qmd
Overhaul demo (#4)
* demo: disable package installation

* reduce dependencies

* Fix yaml

* use project dir as wd

* Change subtitle

* add name placeholders

* demo: reformat

* demo: change theme colour

* demo: update pdf:

---
title: European or American? A re-examination of the transatlantic influence over the IMF
header-includes: |
  \AtBeginDocument{\title[European or American]{European or American? A re-examination of the transatlantic influence over the IMF}}
date: last-modified
author:
- name: Dianyi Yang
# - name: Tong Hu // name placeholders subject to change
# - name: Zhenyi Chen
format:
  beamer:
    theme: Madrid
bibliography: references.bib
csl: extra/apa.csl
---

>>>>

---
title: European or American? A re-examination of the transatlantic influence over the IMF
header-includes: |
  \AtBeginDocument{\title[European or American]{European or American? A re-examination of the transatlantic influence over the IMF}}
date: last-modified
author:
- name: Dianyi Yang
# - name: Tong Hu // name placeholders subject to change
# - name: Zhenyi Chen
format:
  beamer:
    theme: Madrid
    include-in-header: 
      - text: |
          \definecolor{myblue}{RGB}{0, 113, 187}
          \colorlet{beamer@blendedblue}{myblue}
bibliography: references.bib
csl: extra/apa.csl
---
